Untitled

### 2021-08-27 analysis/paper/paper.Rmd
knit first draft... although, still needs abstract

---
title: "Untitled"
author:
  - "Bjørn Peare Bartholdy"
  - Amanda G. Henry
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    #template: "../templates/sn-article-template/sn-article.tex"
    df_print: kable
    toc: no
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
  bookdown::html_document2:
    df_print: kable
    keep_md: true
  bookdown::word_document2:
    reference_docx: "../templates/template.docx"
linestretch: 2.0 # double-spacing for review purposes
bibliography: refs.bib
csl: apa.csl
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
keywords: |
  keyword 1; keyword 2
---

@@

<!-- absolute solution counts compared to absolute sample counts. does exposure
to higher quantities of starches mean more incorporated starches? -->
The separate wheat and potato solutions were made with a 0.25% (w/v) starch
concentration, while the mixed-starch solution was made with 0.25% (w/v) of each
starch, with a total concentration of 0.50% (w/v).
The mixed treatment had the highest absolute count of starch granules in solution (mean = `r subset(count_sol, treatment == "mix")$total`),
while the biofilms exposed to the wheat solution preserved the greatest number of
granules 
(mean = `r subset(count_sample, treatment == "wheat")$total`). 
The potato treatment had the lowest absolute counts in both the solution 
(`r subset(count_sol, treatment == "potato")$total`)
and in the biofilm samples 
(`r subset(count_sample, treatment == "potato")$total`) 
(Tables \@ref(tab:solution-count-tbl) and \@ref(tab:sample-count-tbl)).

>>>>

---
title: "Untitled"
author:
  - "Bjørn Peare Bartholdy"
  - Amanda G. Henry
date: "`r Sys.Date()`"
output:
  bookdown::word_document2:
    reference_docx: "../templates/template.docx"
  bookdown::pdf_document2:
    #template: "../templates/sn-article-template/sn-article.tex"
    df_print: kable
    toc: no
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
  bookdown::html_document2:
    df_print: kable
    keep_md: true
linestretch: 2.0 # double-spacing for review purposes
bibliography: refs.bib
csl: apa.csl
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
keywords: |
  keyword 1; keyword 2
---

@@

<!-- absolute solution counts compared to absolute sample counts. does exposure
to higher quantities of starches mean more incorporated starches? -->
The separate wheat and potato solutions were made with a 0.25% (w/v) starch
concentration, while the mixed-starch solution was made with 0.25% (w/v) of each
starch, with a total concentration of 0.50% (w/v).
The mixed treatment had the highest absolute count of starch granules in solution (mean = `r subset(count_sol, solution == "mix")$total`),
while the biofilms exposed to the wheat solution preserved the greatest number of
granules 
(mean = `r subset(count_sample, treatment == "wheat")$total`). 
The potato treatment had the lowest absolute counts in both the solution 
(`r subset(count_sol, solution == "potato")$total`)
and in the biofilm samples 
(`r subset(count_sample, treatment == "potato")$total`) 
(Tables \@ref(tab:solution-count-tbl) and \@ref(tab:sample-count-tbl)).
